k-Space Domain Parallel Transmit Pulse Design

### 2020-10-25 Manuscript_r2/Theory.tex
wag finished r2

\subsection*{k-Space-Domain Subproblems}
We propose to compute a sparse 
design matrix $\bm{W}$ that directly maps the Fourier transform of a desired spatial 
excitation pattern to a vector of RF pulses that together produce the pattern, as:
\begin{equation}
\bm{b} = \bm{W} \mathcal{F}(\bm{d}),
\end{equation}
where $\bm{b}$ is a vector of concatenated multi-channel RF pulses with length $N_t  N_c$, 
where $N_t$ and $N_c$ are the numbers of time points and channels, respectively,
and $\mathcal{F}(\bm{d})$ is a length-$N_s$ vector containing the 
Fourier transform of the \textcolor{blue}{complex-valued}\revbox{R1.1} target k-space excitation pattern $\bm{d}$.
$\bm{W}$ has dimensions $N_t  N_c \times N_s$.
Once the entries of $\bm{W}$ are computed, 
the RF design problem can be instantaneously solved by a sparse matrix multiplication. 
%without a full matrix inversion or an iterative algorithm. 
Here we describe how to break down the problem of constructing $\bm{W}$ 
into a set of smaller independent subproblems that can be solved in parallel.

@@

\par The columns of $\bm{W}$ can be solved independently, 
based on the observation that if the desired k-space pattern is a delta function at a k-space location 
$\vec{k}_j$ ($1\leq j \leq N_s$), 
then only the $j$-th column $\bm{w}_j$ of $\bm{W}$ is required to relate 
the desired k-space pattern to the desired RF pulse. 
In this case, the vector $\bm{w}_j$ is identical to the desired RF. 
Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be stated as: 
what should the RF pulse samples be to generate a unit delta function at the location $\vec{k}_j$ in k-space, 
and zeros elsewhere? 
Mathematically, the relationship that should be satisfied by the weights in column $\bm{w}_j$  can be expressed as:   
\begin{equation}\label{eq:ScalerForm}
\delta(\vec{k}-\vec{k}_j)=\sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
\end{equation}
where $i$ indexes time points in the pulses' excitation k-space trajectory, 
and $c$ indexes channels. 
$w_c(\vec{k}_i)$ is the $((c-1)N_t+i)$-th element of the $\bm{w}_j$ vector,
and $s_c(\vec{k}-\vec{k}_i)$ is the Fourier transform of channel-$c$'s $B_1^+$ map, 
shifted to be centered at excitation k-space location $\vec{k}_i$. 
Equation \ref{eq:ScalerForm} can be restated in matrix-vector form as:                                       
\begin{equation}\label{eq:MatrixForm}
\bm{Sw}_j=\bm{\delta}_j,
\end{equation}
where $\bm{S}$ is a $N_s \times N_c  N_t$ 
matrix containing values of $s_c(\vec{k}-\vec{k}_i)$ for all $c$ and $i$,
and $\bm{\delta}_j$ is a vector containing a one in the entry corresponding to excitation k-space location
$\vec{k}_j$, and zeros in all other entries. 
The regularized pseudoinverse solution for $\bm{w}_j$ is:                      
\begin{equation}\label{eq:Solution}
\bm{w}_j=\left( \bm{S}^{H} \bm{S} + \lambda \bm{I} \right) ^{-1} \bm{s}_j^{H}
\end{equation}
where $\bm{s}_j^{H}$ is the conjugate transpose of the $j$-th row of $\bm{S}$.

\par If all points on the excitation k-space trajectory are considered in Equation \ref{eq:ScalerForm},
then there is no reduction in computation compared to a conventional pseudoinverse-based pulse design.
However, because $B_1^+$ maps are localized near $\vec{k} = 0$ in excitation k-space,
only a small number ($\ll N_t$) of trajectory points near the target location $\vec{k}_j$ can contribute significantly
to the excitation pattern at $\vec{k}_j$ or its neighbors, 
and therefore need to be considered in the subproblem;
all other trajectory points can be ignored.
This means Equation \ref{eq:ScalerForm} can be modified to:
\begin{equation}
\delta(\vec{k}-\vec{k}_j) = \sum_{\vec{k}_i \in \mathbb{N}}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
\end{equation} 
where $\mathbb{N}$ is the set of trajectory points in the vicinity of $\vec{k}_j$. 
In this work `inclusion width' is defined as the distance, 
in \textcolor{blue}{phase cycles over the excitation field-of-view (cycles/FOV), }\revbox{R1.2} 
from each target location $\vec{k}_j$ within which all trajectory points are accrued into $\mathbb{N}$.
This reduced set of trajectory points reduces the column dimension of $\bm{S}$
and both dimensions of $\bm{S}^H\bm{S}$,
and implies that the design matrix $\bm{W}$ is sparse.
Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$ for a two-dimensional pulse design, 
and the nearby points on the trajectory that need to be included in the solution for $\bm{w}_j$
for an inclusion width of 4 cycles/FOV.

@@

%\subsection*{Efficient construction of $\bm{S}^{H}\bm{S}$ matrix}
\par Constructing the $\bm{S}^{H}\bm{S}$ matrix by first constructing $\bm{S}$ is computationally expensive 
because it requires each channel's $B_1^+$ map to be shifted to each trajectory location $\vec{k}_i$
by phase modulation followed by Fourier transform, or by Fourier transform followed by interpolation. 
Furthermore, 
the matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ is also computationally intensive due to the potentially 
large row dimension of $\bm{S}$, if the zero excitation condition is enforced on a large grid of points around each $\vec{k}_j$.
The computational costs can be reduced by truncating the $B_1^+$ maps in k-space, 
but this introduces large errors. 
Instead, inspired by the non-Cartesian GRAPPA method of Ref \cite{luo2019grappa}, 
we propose to construct the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly via interpolation of the Fourier transforms
of inner products of pairs of $B_1^+$ maps. 
The $\bm{S}^H\bm{S}$ matrix can be written in block form as:
\begin{equation}\label{eq:SHS_blocks}
\bm{S}^{H}\bm{S} = 
\begin{pmatrix}
\bm{S}_1^{H}\bm{S}_1 & \cdots & \bm{S}_1^{H}\bm{S}_{N_c} \\
\vdots  &  \ddots & \vdots  \\
\bm{S}_{N_c}^{H}\bm{S}_1 & \cdots & \bm{S}_{N_c}^{H}\bm{S}_{N_c} 
\end{pmatrix}, 
\end{equation}
where each sub-matrix $\bm{S}_i^H\bm{S}_j$ contains inner products of the Fourier transforms of channel $i$ and channel $j$'s 
$B_1^+$ maps, after they are shifted to be centered different points on the excitation trajectory corresponding to the row 
and column indices of the sub-matrix.
These inner products can be calculated by interpolating the Fourier transform of the dot product of 
channel $i$ and channel $j$'s $B_1^+$ maps. 
In other words, each element in the Hermitian matrix $\bm{S}_i^{H}\bm{S}_j$ 
is the vector sum of channel $i$ and channel $j$'s shifted k-space $B_1^+$ maps, 
which is also a single point of their k-space convolution. 
Via the multiplication property of the Fourier transform, 
this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps. 
For further details, please refer to Ref. \cite{luo2019grappa}.
%In practice, $\bm{S}^{H}\bm{S}$ is constructed in the following way. 
%We first represent the $\bm{S}^{H}\bm{S}$ matrix with block matrices. Each block matrix $\bm{S}_i^{H}\bm{S}_j$ is of size $N_n$ by $N_n$, and $\bm{S}_i$ and $\bm{S}_j$ are the columns of $\bm{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.

\par Since $\bm{S}^{H}\bm{S}$ and its sub-matrices are Hermitian, 
we only need to find the values within the lower triangle of the matrix, 
which are the sub-matrices $\bm{S}_i^{H}\bm{S}_j$ with $i>j$ that are themselves lower triangular. 
The elements of a given sub-matrix $\bm{S}_i^{H}\bm{S}_j$ 
are interpolated from a densely sampled Fourier transform of the dot product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th channels. 
The $(m,n)$-th element is the value interpolated at a position $\vec{k}_m-\vec{k}_n$ away from DC,
where $\vec{k}_m$ and $\vec{k}_n$ are the excitation k-space trajectory locations corresponding to row $m$ and column $n$.
Compared to phase-modulating and Fourier transforming each channel's $B_1^+$ map for each point 
on the trajectory which would require $N_t  N_c$ Fourier transforms,
to solve all the columns of $\bm{W}$ the total number of Fourier transforms needed in this efficient method is $N_c(N_c+1)/2$. 
The storage size is also much smaller, 
and the matrix multiplication between $\bm{S}^H$ and $\bm{S}$ is avoided.
%An alternative strategy would be to construct $\bm{S}$ by Fourier transforming each channel's $B_1^+$ map 
%and then interpolating it to be centered at each trajectory location, 
%but this again requires multiplication of the $\bm{S}^{H}$ and $\bm{S}$ matrices,
%which further involves the multiplication of interpolated values. 
%We have found empirically that this strategy introduces higher error
%than interpolating the inner product values. 
%Furthermore, to calculate each element of $\bm{S}^{H}\bm{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy. While with the efficient algorithm there is only one interpolation from the densely sampled Fourier Transform of the dot product of two spatial domain $B_1^+$ maps needed. The extra interpolations involved in the sub-optimal strategy would introduce a larger error to $\bm{S}^{H}\bm{S}$.

\subsection*{Off-Resonance Compensation}
% In order to model the off-resonance into our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}. 
Off-resonance compensation is common in spatial-domain parallel pulse designs \cite{Grissom:2006:MRM}, 
but has not been previously implemented in a k-space-domain design.
Spatial domain designs based on NUFFTs make use of an approximate time-segmented
model for the off-resonance term \cite{fessler2005toeplitz},
which decouples the space- and time-dependence of off-resonant phase accrual into the product of 
space- and time-dependent terms, which are applied on either side of the NUFFT operator. 
Here we show how a time-segmented off-resonance model can be incorporated in the proposed k-space-domain algorithm. 
Mathematically, the time-segmented model is given by:
\textcolor{blue}{
\begin{equation}
e^{\imath \Delta\omega(\vec{x}_j) (t_i-T) }\approx\sum_{l=1}^{L} b_l(t_i) h_{l}(\vec{x}_j) ,
\end{equation}
where $\Delta\omega(\vec{x}_j)$ is the off-resonance frequency at $\vec{x}_j$, 
$i$ indexes time points in the pulse, 
$T$ is the pulse duration,
and $l$ indexes the $L$ time segments, where $L$ is typically between 4 and 8. 
The $b_{l}(t_i)$ functions are temporal interpolators that multiply into the RF samples and are determined by
numerical optimization as described in Ref. \cite{fessler2005toeplitz},
and $h_{l}(\vec{x}_j) = e^{\imath \Delta\omega(\vec{x}_j)\breve{t}_l}$ are the off-resonance phase shifts 
applied to the excitation patterns produced by the RF pulse time segments centered at time points $\{\breve{t}_l: l = 1, \dots, L\}$.
The time-segmented off-resonance model can be incorporated into Equation \ref{eq:ScalerForm} as:
\begin{equation}
	\delta(\vec{k}-\vec{k}_j)=\sum_{l = 1}^L \sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) b_l(t_i) \tilde{s}_{cl} (\vec{k}-\vec{k}_i), 
\end{equation}
where $\tilde{s}_{cl}(\vec{k})$ is the Fourier transform of the product of channel $c$'s $B_1^+$ map and time segment $l$'s 
off-resonance phase shift $h_l(\vec{x}_j)$. 
We can then write the equivalent of Equation \ref{eq:MatrixForm} with the off-resonance model:
\begin{equation}
	\sum_{l=1}^L \bm{S}_l \textrm{diag}(b_{l}(t_i)) \bm{w}_j = \bm{\delta}_j,
\end{equation} 
where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and $h_l(\vec{x}_j)$ products.} \revbox{R1.3}  
Efficient construction of the $\bm{S}^{H}\bm{S}$ matrix follows much the same procedure as without
off-resonance except that with off-resonance,
the elements of each sub-matrix $\bm{S}_i^{H}\bm{S}_j$ in Equation \ref{eq:SHS_blocks}
are interpolated from $L(L+1)/2$ Fourier transformed maps,
and the interpolated values are weighted by the temporal interpolators for each pair of multiplied time segments before they 
are summed.
Compared to constructing $\bm{S}^H\bm{S}$ without off-resonance, 
taking off-resonance into account increases the total number of FFT operations form $N_c(N_c+1)/2$ to $N_cL(N_cL+1)/2$, 
and increases the number of interpolations needed for each sub-matrix element from 1 to $L(L+1)/2$.  
However, we note that only adjacent time segments with overlapping temporal interpolators at a given time point
need to be considered when calculating the elements of $\bm{S}^H\bm{S}$ corresponding to that time point.

>>>>

\subsection*{k-Space-Domain Subproblems}
We propose to compute a sparse 
design matrix $\bm{W}$ that directly maps the Fourier transform of a desired spatial 
excitation pattern to a vector of RF pulses that together produce the pattern, as:
\begin{equation}
\bm{b} = \bm{W} \mathcal{F}(\bm{d}),
\end{equation}
where $\bm{b}$ is a vector of concatenated multi-channel RF pulses with length $N_t  N_c$, 
where $N_t$ and $N_c$ are the numbers of time points and channels, respectively,
and $\mathcal{F}(\bm{d})$ is a length-$N_s$ vector containing the 
Fourier transform of the complex-valued target k-space excitation pattern $\bm{d}$.
$\bm{W}$ has dimensions $N_t  N_c \times N_s$.
Once the entries of $\bm{W}$ are computed, 
the RF design problem can be instantaneously solved by a sparse matrix multiplication. 
%without a full matrix inversion or an iterative algorithm. 
Here we describe how to break down the problem of constructing $\bm{W}$ 
into a set of smaller independent subproblems that can be solved in parallel.

@@

\par The columns of $\bm{W}$ can be solved independently, 
based on the observation that if the desired k-space pattern is a delta function at a k-space location 
$\vec{k}_j$ ($1\leq j \leq N_s$), 
then only the $j$-th column $\bm{w}_j$ of $\bm{W}$ is required to relate 
the desired k-space pattern to the desired RF pulse. 
In this case, the vector $\bm{w}_j$ is identical to the desired RF. 
Therefore, the problem of finding the $j$-th column $\bm{w}_j$ of $\bm{W}$ can be stated as: 
what should the RF pulse samples be to generate a unit delta function at $\vec{k}_j$, 
and zeros elsewhere? 
Mathematically, the relationship that should be satisfied by the weights in column $\bm{w}_j$  can be expressed as:   
\begin{equation}\label{eq:ScalerForm}
\delta(\vec{k}-\vec{k}_j)=\sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
\end{equation}
where $i$ indexes time points in the pulses' excitation k-space trajectory, 
and $c$ indexes channels. 
$w_c(\vec{k}_i)$ is the $((c-1)N_t+i)$-th element of the $\bm{w}_j$ vector,
and $s_c(\vec{k}-\vec{k}_i)$ is the Fourier transform of channel-$c$'s $B_1^+$ map, 
shifted to be centered at excitation k-space location $\vec{k}_i$. 
Equation \ref{eq:ScalerForm} can be restated in matrix-vector form as:                                       
\begin{equation}\label{eq:MatrixForm}
\bm{Sw}_j=\bm{e}_j,
\end{equation}
where $\bm{S}$ is a $N_s \times N_c  N_t$ 
matrix containing values of $s_c(\vec{k}-\vec{k}_i)$ for all $c$ and $i$,
and $\bm{e}_j$ is a vector containing a one in the entry corresponding to excitation k-space location
$\vec{k}_j$, and zeros in all other entries. 
The regularized pseudoinverse solution for $\bm{w}_j$ is:                      
\begin{equation}\label{eq:Solution}
\bm{w}_j=\left( \bm{S}^{H} \bm{S} + \lambda \bm{I} \right) ^{-1} \bm{s}_j^{H}
\end{equation}
where $\bm{s}_j^{H}$ is the conjugate transpose of the $j$-th row of $\bm{S}$.

\par If all points on the excitation k-space trajectory are considered in Equation \ref{eq:ScalerForm},
then there is no reduction in computation compared to a conventional pseudoinverse-based pulse design.
However, because $B_1^+$ maps are localized near $\vec{k} = 0$ in excitation k-space,
only a small number ($\ll N_t$) of trajectory points near the target location $\vec{k}_j$ can contribute significantly
to the excitation pattern at $\vec{k}_j$ or its neighbors, 
and therefore need to be considered in the subproblem;
all other trajectory points can be ignored.
This means Equation \ref{eq:ScalerForm} can be modified to:
\begin{equation}
\delta(\vec{k}-\vec{k}_j) = \sum_{\vec{k}_i \in \mathbb{N}}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
\end{equation} 
where $\mathbb{N}$ is the set of trajectory points in the vicinity of $\vec{k}_j$. 
In this work `inclusion width' is defined as the distance, 
in phase cycles over the excitation field-of-view (cycles/FOV), 
from each target location $\vec{k}_j$ within which all trajectory points are accrued into $\mathbb{N}$.
This reduced set of trajectory points reduces the column dimension of $\bm{S}$
and both dimensions of $\bm{S}^H\bm{S}$,
and implies that the design matrix $\bm{W}$ is sparse.
Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$ for a two-dimensional pulse design, 
and the nearby points on the trajectory that need to be included in the solution for $\bm{w}_j$
for an inclusion width of 4 cycles/FOV.

@@

%\subsection*{Efficient construction of $\bm{S}^{H}\bm{S}$ matrix}
\par Constructing the $\bm{S}^{H}\bm{S}$ matrix by first constructing $\bm{S}$ is computationally expensive 
because it requires each channel's $B_1^+$ map to be shifted to each trajectory location $\vec{k}_i$
by phase modulation followed by Fourier transform, or by Fourier transform followed by interpolation. 
Furthermore, 
the matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ is also computationally intensive due to the potentially 
large row dimension of $\bm{S}$, if the zero excitation condition is enforced on a large grid of points around each $\vec{k}_j$.
The computational costs can be reduced by truncating the $B_1^+$ maps in k-space, 
but this introduces large errors. 
Instead, inspired by the non-Cartesian GRAPPA method of Ref \cite{luo2019grappa}, 
we propose to construct the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly via interpolation of the Fourier transforms
of inner products of pairs of $B_1^+$ maps. 
The $\bm{S}^H\bm{S}$ matrix can be written in block form as:
\begin{equation}\label{eq:SHS_blocks}
\bm{S}^{H}\bm{S} = 
\begin{pmatrix}
\bm{S}_1^{H}\bm{S}_1 & \cdots & \bm{S}_1^{H}\bm{S}_{N_c} \\
\vdots  &  \ddots & \vdots  \\
\bm{S}_{N_c}^{H}\bm{S}_1 & \cdots & \bm{S}_{N_c}^{H}\bm{S}_{N_c} 
\end{pmatrix}, 
\end{equation}
where each sub-matrix $\bm{S}_i^H\bm{S}_j$ contains inner products of the Fourier transforms of channel $i$ and channel $j$'s 
$B_1^+$ maps, after they are shifted to be centered different points on the excitation trajectory corresponding to the row 
and column indices of the sub-matrix.
These inner products can be calculated by interpolating the Fourier transform of the product of 
channel $i$ and channel $j$'s $B_1^+$ maps. 
In other words, each element in the Hermitian matrix $\bm{S}_i^{H}\bm{S}_j$ 
is the vector sum of channel $i$ and channel $j$'s shifted k-space $B_1^+$ maps, 
which is also a single point of their k-space convolution. 
Via the multiplication property of the Fourier transform, 
this convolution in k-space can be calculated from the Fourier transform of the product of the two spatial domain $B_1^+$ maps. 
For further details, please refer to Ref. \cite{luo2019grappa}.
%In practice, $\bm{S}^{H}\bm{S}$ is constructed in the following way. 
%We first represent the $\bm{S}^{H}\bm{S}$ matrix with block matrices. Each block matrix $\bm{S}_i^{H}\bm{S}_j$ is of size $N_n$ by $N_n$, and $\bm{S}_i$ and $\bm{S}_j$ are the columns of $\bm{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.

\par Since $\bm{S}^{H}\bm{S}$ is Hermitian, 
we only need to find the values within the lower triangle of the matrix, 
which are the sub-matrices $\bm{S}_i^{H}\bm{S}_j$ with $i>j$. % that are themselves lower triangular. 
The elements of a given sub-matrix $\bm{S}_i^{H}\bm{S}_j$ 
are interpolated from a densely sampled Fourier transform of the product of the spatial domain $B_1^+$ maps of the $i$-th and $j$-th channels. 
The $(m,n)$-th element is the value interpolated at a position $\vec{k}_m-\vec{k}_n$ away from DC,
where $\vec{k}_m$ and $\vec{k}_n$ are the excitation k-space trajectory locations corresponding to row $m$ and column $n$.
Compared to phase-modulating and Fourier transforming each channel's $B_1^+$ map for each point 
on the trajectory which would require $N_t  N_c$ Fourier transforms,
to solve all the columns of $\bm{W}$ the total number of Fourier transforms needed in this efficient method is $N_c(N_c+1)/2$. 
The storage size is also much smaller, 
and the matrix multiplication between $\bm{S}^H$ and $\bm{S}$ is avoided.
%An alternative strategy would be to construct $\bm{S}$ by Fourier transforming each channel's $B_1^+$ map 
%and then interpolating it to be centered at each trajectory location, 
%but this again requires multiplication of the $\bm{S}^{H}$ and $\bm{S}$ matrices,
%which further involves the multiplication of interpolated values. 
%We have found empirically that this strategy introduces higher error
%than interpolating the inner product values. 
%Furthermore, to calculate each element of $\bm{S}^{H}\bm{S}$, there are $2N_s$ number of interpolations involved with this sub-optimal strategy. While with the efficient algorithm there is only one interpolation from the densely sampled Fourier Transform of the dot product of two spatial domain $B_1^+$ maps needed. The extra interpolations involved in the sub-optimal strategy would introduce a larger error to $\bm{S}^{H}\bm{S}$.

\subsection*{Off-Resonance Compensation}
% In order to model the off-resonance into our k-space domain design, we adapted a fast implementation of the off-resonance compensation with time segmentation approximation and weighted least-squares interpolators \cite{fessler2005toeplitz}. 
Off-resonance compensation is common in spatial-domain parallel pulse designs \cite{Grissom:2006:MRM}, 
but has not been previously implemented in a k-space-domain design.
Spatial domain designs based on NUFFTs make use of an approximate time-segmented
model for the off-resonance term \cite{fessler2005toeplitz},
which decouples the space- and time-dependence of off-resonant phase accrual into the product of 
space- and time-dependent terms, which are applied on either side of the NUFFT operator. 
Here we show how a time-segmented off-resonance model can be incorporated in the proposed k-space-domain algorithm. 
Mathematically, the time-segmented model is given by:
\begin{equation}
e^{\imath \Delta\omega(\vec{x}_j) (t_i-T) }\approx\sum_{l=1}^{L} b_l(t_i) h_{l}(\vec{x}_j) ,
\end{equation}
where $\Delta\omega(\vec{x}_j)$ is the off-resonance frequency at $\vec{x}_j$, 
$i$ indexes time points in the pulse, 
$T$ is the pulse duration,
and $l$ indexes the $L$ time segments, where $L$ is typically between 4 and 8. 
The $b_{l}(t_i)$ functions are temporal interpolators that multiply into the RF samples and are determined by
numerical optimization as described in Ref. \cite{fessler2005toeplitz},
and $h_{l}(\vec{x}_j) = e^{\imath \Delta\omega(\vec{x}_j)\breve{t}_l}$ are the off-resonance phase shifts 
applied to the excitation patterns produced by the RF pulse time segments centered at time points $\{\breve{t}_l: l = 1, \dots, L\}$.
The time-segmented off-resonance model can be incorporated into Equation \ref{eq:ScalerForm} as:
\begin{equation}
	\delta(\vec{k}-\vec{k}_j)=\sum_{l = 1}^L \sum_{i=1}^{N_t}\sum_{c=1}^{N_c} w_c(\vec{k}_i) b_l(t_i) \tilde{s}_{cl} (\vec{k}-\vec{k}_i), 
\end{equation}
where $\tilde{s}_{cl}(\vec{k})$ is the Fourier transform of the product of channel $c$'s $B_1^+$ map and time segment $l$'s 
off-resonance phase shift $h_l(\vec{x}_j)$. 
We can then write the equivalent of Equation \ref{eq:MatrixForm} with the off-resonance model:
\begin{equation}
	\sum_{l=1}^L \bm{S}_l \textrm{diag}(b_{l}(t_i)) \bm{w}_j = \bm{e}_j,
\end{equation} 
where the matrix $\bm{S}_l$ is now formed from the $N_c  L$ Fourier transforms of the $B_1^+$ map and $h_l(\vec{x}_j)$ products.  
Efficient construction of the $\bm{S}^{H}\bm{S}$ matrix follows much the same procedure as without
off-resonance except that with off-resonance,
the elements of each sub-matrix $\bm{S}_i^{H}\bm{S}_j$ in Equation \ref{eq:SHS_blocks}
are interpolated from $L(L+1)/2$ Fourier transformed maps,
and the interpolated values are weighted by the temporal interpolators for each pair of multiplied time segments before they 
are summed.
Compared to constructing $\bm{S}^H\bm{S}$ without off-resonance, 
taking off-resonance into account increases the total number of FFT operations form $N_c(N_c+1)/2$ to $N_cL(N_cL+1)/2$, 
and increases the number of interpolations needed for each sub-matrix element from 1 to $L(L+1)/2$.  
However, we note that only adjacent time segments with overlapping temporal interpolators at a given time point
need to be considered when calculating the elements of $\bm{S}^H\bm{S}$ corresponding to that time point.

### 2020-10-25 Manuscript_r2/kPtx_paper.tex
wag finished r2

% the following command can be used to mark changes made due to reviewers' concerns. Use as \revbox{Rx.y} for reviewer x, concern y.
\newif\ifmarkedup
\markeduptrue

@@

\section*{\underline{Abstract}} 
{\bf Purpose:}
To accelerate the design of \textcolor{blue}{(under- or oversampled)}\revbox{R1.4} multidimensional parallel transmission pulses. 
\\[1em]
{\bf Methods:}
A k-space domain parallel transmission pulse design algorithm was proposed that
produces a sparse matrix relating a \textcolor{blue}{complex-valued}\revbox{R1.1} target excitation pattern to the pulses that produce it, 
and can be finely parallelized. 
The algorithm was applied in simulations to the design of 3D SPINS pulses for inner volume excitation in the brain at 7 Tesla.
It was characterized in terms of the dependence of computation time, excitation error, and required memory
on algorithm parameters,
and it was compared to the spatial domain pulse design method in terms of computation time, excitation error,
Gibbs ringing, and ability to compensate off-resonance.
\\[1em]
{\bf Results:}
The proposed algorithm achieved approximately 80\% faster pulse design compared to 
an iterative spatial domain method, with the same number of parallel threads,
with the tradeoff of increased excitation error and RMS RF amplitude. 
It reduced the memory required to store the design matrix by 99\% compared to a full matrix solution.
Even with a coarse design grid, the algorithm produced patterns that were free of Gibbs ringing.
It was similarly sensitive to k-space undersampling as the spatial domain method,
and was similarly capable of compensating for off-resonance.
\\[1em]
{\bf Conclusion:}
The proposed k-space domain algorithm accelerates and finely parallelizes parallel transmission pulse design,
with a modest tradeoff of excitation error and RMS RF amplitude.
\\[1em]
{\bf \noindent Key words:} Parallel Transmission; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation.

@@

\begin{figure}[!h]
	\centering
	%\includegraphics[width=\textwidth]{kspace_PTX_Patch}
	\caption{(a) A target point $\vec{k}_j$ and the nearby trajectory points that are included when calculating 
	RF pulse weight contributions from this point.
	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
	or patches of target points can be solved for jointly. 
	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 patch of target points are solved together,
	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 region
	centered on the patch are considered in the calculation.}
	\label{fig:Patch}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	%\includegraphics[width=\textwidth]{ComputationTime}
	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4 cycles/FOV. 
	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 cycles/FOV, and 16 threads.}
	\label{fig:ComputationTime}
\end{figure}

\begin{figure}[!h]
	\centering
	%\includegraphics[width=\textwidth]{L_curve}
	\caption{L-curves for spatial domain and k-space domain pulse designs, 
	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Patch / Inclusion Widths = 4' versus `Patch / Inclusion Widths = $\infty$'),
	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated Matrices' versus
	`Exact Matrices').}
	\label{fig:LCurves}
\end{figure}

>>>>

% the following command can be used to mark changes made due to reviewers' concerns. Use as \revbox{Rx.y} for reviewer x, concern y.
\newif\ifmarkedup
%\markeduptrue

@@

\section*{\underline{Abstract}} 
{\bf Purpose:}
To accelerate the design of (under- or oversampled) multidimensional parallel transmission pulses. 
\\[1em]
{\bf Methods:}
A k-space domain parallel transmission pulse design algorithm was proposed that
produces a sparse matrix relating a complex-valued target excitation pattern to the pulses that produce it, 
and can be finely parallelized. 
The algorithm was applied in simulations to the design of 3D SPINS pulses for inner volume excitation in the brain at 7 Tesla.
It was characterized in terms of the dependence of computation time, excitation error, and required memory
on algorithm parameters,
and it was compared to an iterative spatial domain pulse design method in terms of computation time, excitation error,
Gibbs ringing, and ability to compensate off-resonance.
\\[1em]
{\bf Results:}
The proposed algorithm achieved approximately 80\% faster pulse design compared to 
the spatial domain method with the same number of parallel threads,
with the tradeoff of increased excitation error and RMS RF amplitude. 
It reduced the memory required to store the design matrix by 99\% compared to a full matrix solution.
Even with a coarse design grid, the algorithm produced patterns that were free of Gibbs ringing.
It was similarly sensitive to k-space undersampling as the spatial domain method,
and was similarly capable of compensating for off-resonance.
\\[1em]
{\bf Conclusion:}
The proposed k-space domain algorithm accelerates and finely parallelizes parallel transmission pulse design,
with a modest tradeoff of excitation error and RMS RF amplitude.
\\[1em]
{\bf \noindent Key words:} Parallel Transmission; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation.

@@

\begin{figure}[!h]
	\centering
	%\includegraphics[width=\textwidth]{kspace_PTX_Patch}
	\caption{(a) A target point $\vec{k}_j$ and the nearby trajectory points that are included when calculating 
	RF pulse weight contributions from this point.
	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
	or patches of target points can be solved for jointly. 
	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 (cycles/FOV)$^2$ patch of target points are solved together,
	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 (cycles/FOV)$^2$ region
	centered on the patch are considered in the calculation.}
	\label{fig:Patch}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	%\includegraphics[width=\textwidth]{ComputationTime}
	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4 cycles/FOV. 
	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for a patch width of 4 cycles/FOV, and 16 threads.}
	\label{fig:ComputationTime}
\end{figure}

\begin{figure}[!h]
	\centering
	%\includegraphics[width=\textwidth]{L_curve}
	\caption{L-curves for spatial domain and k-space domain pulse designs, 
	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
	The k-space domain designs were repeated using patch and inclusion widths of 4 cycles/FOV versus solving for the entire domain at once (`Patch / Inclusion Widths = 4' versus `Patch / Inclusion Widths = $\infty$'),
	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated Matrices' versus
	`Exact Matrices').}
	\label{fig:LCurves}
\end{figure}
